Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_3-microservice.tex
Capitalize only the proper nouns

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{WDIAS architecture to handle request asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{Weather Data Integration and Assimilation System Architecture for Server Requests on Demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{Weather Data Integration and Assimilation System Architecture for Handle Request Asynchronously}
    \label{fi:wdias_micro_async}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation of WDIAS microservices}
    \label{fi:wdias_micro_separation}
\end{figure}

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture to handle request asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture for server requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handle request asynchronously}
    \label{fi:wdias_micro_async}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation \acrshort{wdias} microservices}
    \label{fi:wdias_micro_separation}
\end{figure}
